Flattering Advice: Avoiding Disappointment in Advice-Giving

### 2025-01-10 manuscript/manuscript.qmd
Add citations to the first paragraph.

keywords: [Gender difference, Advice, Interpresonal relationship]
bibliography: bibliography.bib
floatsintext: true
mask: false
link-citations: false
format:
  apaquarto-html: default
  apaquarto-pdf:
    documentmode: man
    keep-tex: true
    prefer-html: true
  apaquarto-docx:
    default: true
    prefer-html: true
---

@@

Career trajectories for men and women often differ substantially, even among those with similar qualifications. One source of such differences may be the advice that people receive. Prior work has documented that men receive more aspirational advice and women more risk-averse advice, which may explain why women are less likely to apply for and ultimately obtain more rewarding positions (Kanze et al., 2018). Research on gender discrimination has focused on the role of unconscious bias (Greenwald et al., 2009; Greenwald & Banaji, 1995), but interventions that try to reduce this bias have been largely unsuccessful (Chang et al., 2019; Paluck & Green, 2009). Recent work has proposed cognitive, rather than unconscious, biases that can lead to gender discrimination through the formation of false beliefs (Hagmann et al., 2024). Here, we propose a novel source of differences in advice by drawing on recent work on belief-based utility, expectation-based reference points (Köszegi, 2006; Kőszegi & Rabin, 2009), and the hedonic consequences of information (Golman et al., 2017).

>>>>

keywords: [Gender difference, Advice, Interpresonal relationship]
bibliography: bibliography.bib
floatsintext: true
mask: false
link-citations: false
format:
  apaquarto-html: default
  apaquarto-pdf:
    documentmode: man
    keep-tex: true
    prefer-html: true
  apaquarto-docx:
    default: true
    prefer-html: true
editor: 
  markdown: 
    wrap: 72
---

@@

Career trajectories for men and women often differ substantially, even
among those with similar qualifications. One source of such differences
may be the advice that people receive. Prior work has documented that
men receive more aspirational advice and women more risk-averse advice,
which may explain why women are less likely to apply for and ultimately
obtain more rewarding positions [@Kanze2018]. Research on gender
discrimination has focused on the role of unconscious bias
[@Greenwald2009; @Greenwald1995], but interventions that try to reduce
this bias have been largely unsuccessful [@Chang2019; @Paluck2009].
Recent work has proposed cognitive, rather than unconscious, biases that
can lead to gender discrimination through the formation of false beliefs
[@Hagmann2024]. Here, we propose a novel source of differences in advice
by drawing on recent work on belief-based utility, expectation-based
reference points [@Koszegi2006; @Koszegi2009], and the hedonic
consequences of information [@Golman2017].
